Detecting Facial Expressions in Professional Tennis Matches

### 2017-02-24 Report06-12.Rmd
Edits to code

#plot images with overlaid boxes
overlayGgplot <- function(imgList, mergeData, matchBox=FALSE){
  for(i in imgList){

    img <- image_read(paste0("images/", i))

@@

    if(nrow(faceData) == 0){
      return(p)
    } else{

@@

    }
    if(matchBox){
      p <- p + geom_path(aes(x=x, y=450-y, group = c(type, boxID), colour=boxID), faceData) + guides(colour="none")
    }
    else{
      p <- p + geom_path(aes(x=x, y=450-y, group = c(FaceID), colour=type), faceData) + scale_color_manual(values = c(Skybiometry="#ffe093", Microsoft="#5cc3f6", Google="#5cba82", Animetrics="#FF959c", Manual="#db70ff"))
    }
  return(p)
  }
}

@@

ALLmetaIMG$detect<-factor(ALLmetaIMG$detect, levels = 0:3, labels = c("Player", "Other staff on court", "Fan", "None"))
ALLmetaIMG$obscured<-factor(ALLmetaIMG$obscured, levels = 0:1, labels = c("No", "Yes"))
ALLmetaIMG$lighting<-factor(ALLmetaIMG$lighting, levels = 0:2, labels = c("Direct sunlight", "Shaded", "Partially shaded"))
ALLmetaIMG$headangle<-factor(ALLmetaIMG$headangle, levels = 0:3, labels = c("Front on", "Back of head", "Profile", "Other"))
ALLmetaIMG$glasses<-factor(ALLmetaIMG$glasses, levels = 0:1, labels = c("No", "Yes"))
ALLmetaIMG$visorhat<-factor(ALLmetaIMG$visorhat, levels = 0:1, labels = c("No", "Yes"))

>>>>

#plot images with overlaid boxes
overlayGgplot <- function(imgList, mergeData, matchBox=FALSE){
  for(i in imgList){
    img <- image_read(paste0("images/", i))

@@

    if(nrow(faceData) == 0){
      print(p)
      next
    } else{

@@

    }
    if(matchBox){
      p <- p + geom_path(aes(x=x, y=450-y, group = c(type, boxID), colour=boxID), faceData) + guides(colour="none")
    }
    else{
      p <- p + geom_path(aes(x=x, y=450-y, group = c(FaceID), colour=type), faceData) + scale_color_manual(values = c(Skybiometry="#ffe093", Microsoft="#5cc3f6", Google="#5cba82", Animetrics="#FF959c", Manual="#db70ff"))
    } 
  print(p)
  }
}

@@

ALLmetaIMG$detect<-factor(ALLmetaIMG$detect, levels = 0:2, labels = c("Player", "Other staff on court", "Fan"))
ALLmetaIMG$obscured<-factor(ALLmetaIMG$obscured, levels = 0:1, labels = c("No", "Yes"))
ALLmetaIMG$lighting<-factor(ALLmetaIMG$lighting, levels = 0:2, labels = c("Direct sunlight", "Shaded", "Partially shaded"))
ALLmetaIMG$headangle<-factor(ALLmetaIMG$headangle, levels = 0:3, labels = c("Front on", "Back of head", "Profile", "Other"))
ALLmetaIMG$glasses<-factor(ALLmetaIMG$glasses, levels = 0:1, labels = c("No", "Yes"))
ALLmetaIMG$visorhat<-factor(ALLmetaIMG$visorhat, levels = 0:1, labels = c("No", "Yes"))
